Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-16 cav2017/cav2017.tex
+contributions

@@

We consider physical models expressed as ordinary differential equations (ODEs) with full state information:  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t)\ \ :\ \ x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}
\end{align}
where $A$ and $B$ are matrices that fully specify the continuous plant.  
\todo{[specify initial conditions? specify input ranges already here? ]} 
Eq.~\eqref{eq:ode} is soundly discretised (as shown in the Appendix \todo{[there we can present directly the full LTI case with outputs]}) into
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k. 
\end{align}
%
The

@@

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback can be employed to affect the properties and behaviours of the process. 
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
The most basec feedback architecture is the state feedback, 
where the control action $\vec{u}_k$ is computed by: 
%
\begin{equation}
u_k = r_{k} - K x_k, 
\end{equation}
%
where $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
and $r_{k}$ is a reference signal.   
%
The closed-loop model then takes the form 
\begin{align}
x_{k+1} = ( A_d - B_d K ) + B_d r_k. \nonumber
\end{align}
The gain matrix $K$ can be set so that the closed-loop dynamics are shaped as desired, 
according to a desired goal or objective. 
A standard objective is to obtain stable closed-loop dynamics.

@@

\todo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantisation noises yet).]}

@@

Jury's criteria is a mathematical method used to verify whether the roots 
of the polynomial are within the unit circle by exploring solely the coefficients 
of the polynomial. In order to achieve this, we first create a matrix 
$\mat{M} \in \mathbb{R}^{(n+1) \times (n+1)}$ with zero-indexed coefficients 
$m_{i,j} : i,j \in [0,n],k=n-(i-1)$ in the following form:
%
\begin{equation}
\left[\begin{array}{ccccc}
c_0&c_1&\hdots&c_{n-1}&c_n\\
m_{\scriptscriptstyle 0,0}-m_{\scriptscriptstyle 0,n}^*\frac{m_{0,n}^*}{m_{0,0}}&m_{\scriptscriptstyle 0,1}-m_{\scriptscriptstyle 0,n-1}^*\frac{m_{0,n}^*}{m_{0,0}}&\hdots&m_{\scriptscriptstyle 0,n-1}-m_{\scriptscriptstyle 0,1}^*\frac{m_{0,n}^*}{m_{0,0}}&0\\
\vdots&\vdots&\vdots&\vdots&\vdots\\
m_{\scriptscriptstyle i-1,0}-m_{\scriptscriptstyle i-1,k-j}^*\frac{m_{i-1,k}^*}{m_{i-1,0}}&m_{\scriptscriptstyle i-1,1}-m_{\scriptscriptstyle i-1,k-j}^*\frac{m_{i-1,k}^*}{m_{i-1,0}}&\hdots&0&0\\
m_{\scriptscriptstyle n-1,0}-m_{\scriptscriptstyle n-1,1-j}^*\frac{m_{n-1,1}^*}{m_{n-1,0}}&0&\hdots&0&0\\
\end{array}\right]
\end{equation}

The first row corresponds to the coefficients of the original polynomial. 
Notice also that every row has a polynomial one degree lower than the previous. 
The sufficient and necessary conditions for the polynomial in row $0$ 
to have all of its roots inside the unit circle are~\cite{astrom1997computer}:
%
\begin{align}
|c_n|<c_0&&
\sum_{i=0}^n c_i > 0&&
(-1)^n\sum_{i=0}^n c_i (-1)^{n-i}> 0&&
m_{i,0}>0
\end{align}

>>>>

\todo{Add contributions (Cristina)}

@@

We consider physical models expressed as ordinary differential equations (ODEs) with full state information:  
%
\begin{align}
\label{eq:ode}
\dot{x}(t) = Ax(t)+ B u(t)\ \ :\ \ x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}
\end{align}
where $A$ and $B$ are matrices that fully specify the continuous plant.  
\todo{[specify initial conditions? specify input ranges already here? ]} 
Eq.~\eqref{eq:ode} is soundly discretised (as shown in the Appendix \todo{[there we can present directly the full LTI case with outputs]}) into
%
\begin{align}
\label{eq:plant}
x_{k+1} = A_d x_k+ B_d u_k. 
\end{align}
%

@@

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback can be employed to affect the properties and behaviours of the process. 
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
The most basic feedback architecture is the state feedback, 
where the control action $\vec{u}_k$ is computed by: 
%
\begin{equation}
u_k = r_{k} - K x_k, 
\end{equation}
%
where $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
and $r_{k}$ is a reference signal.   
%
The closed-loop model then takes the form 
\begin{align}
x_{k+1} = ( A_d - B_d K ) + B_d r_k. \nonumber
\end{align}
The gain matrix $K$ can be set so that the closed-loop dynamics are shaped as desired, 
according to a desired goal or objective. 
A standard objective is to obtain stable closed-loop dynamics.

@@

%\todo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantisation noises yet).]}

Jury's criterion is a mathematical method used to verify whether the roots 
of a characteristic polynomial are within the unit circle by exploring solely the coefficients 
of the polynomial. The first step is to create a matrix 
$\mat{M} \in \mathbb{R}^{(n+1) \times (n+1)}$ with the first row elements 
$m_{0,j}=c_j$, where $j \in [0,n]$, $k=n-(i-1)$ and 
$c_j$ are the coefficients of the original polynomial. 
%
\begin{equation}
\left[\begin{array}{ccccc}
c_0&c_1&\hdots&c_{n-1}&c_n\\
m_{\scriptscriptstyle 0,0}-m_{\scriptscriptstyle 0,n}^*\frac{m_{0,n}^*}{m_{0,0}}&m_{\scriptscriptstyle 0,1}-m_{\scriptscriptstyle 0,n-1}^*\frac{m_{0,n}^*}{m_{0,0}}&\hdots&m_{\scriptscriptstyle 0,n-1}-m_{\scriptscriptstyle 0,1}^*\frac{m_{0,n}^*}{m_{0,0}}&0\\
\vdots&\vdots&\vdots&\vdots&\vdots\\
m_{\scriptscriptstyle i-1,0}-m_{\scriptscriptstyle i-1,k-j}^*\frac{m_{i-1,k}^*}{m_{i-1,0}}&m_{\scriptscriptstyle i-1,1}-m_{\scriptscriptstyle i-1,k-j}^*\frac{m_{i-1,k}^*}{m_{i-1,0}}&\hdots&0&0\\
m_{\scriptscriptstyle n-1,0}-m_{\scriptscriptstyle n-1,1-j}^*\frac{m_{n-1,1}^*}{m_{n-1,0}}&0&\hdots&0&0\\
\end{array}\right]
\end{equation}

Notice that every row has a polynomial one degree lower than the previous. 
The sufficient and necessary conditions for the polynomial in row $0$ 
to have all of its roots inside the unit circle are~(\cite{astrom1997computer}):
%
\begin{align}
|c_n|<c_0&&
\sum_{i=0}^n c_i > 0&&
(-1)^n\sum_{i=0}^n c_i (-1)^{n-i}> 0&&
m_{i,0}>0
\end{align}

@@
